Birth Spacing in the Presence of Son Preference and Sex-Selective \\ Abortions: India's Experience over Four Decades

### 2018-04-19 presentations/2018-paa-poster.tex
Shorten method and data blocks

The model is a discrete time, non-proportional, competing risk 
hazard model with two exit states: either a boy or a girl is born.
\begin{itemize}
\item the competing risk framework captures that access to prenatal 
sex determination means that parents can choose the sex of children born.
\item the non-proportional hazard specification captures that  
sex composition and the use of sex selection are likely to affect 
the shape of the hazard functions across groups.
\end{itemize}

@@

The data come from the four rounds of the National Family Health Survey.

I exclude visitors to the household, as well as
women who have never been married or married more than once, divorced, or who are 
not living with their husband,
women with inconsistent age at marriage,
and those with missing information on education.
The same goes for women who had at least one multiple births,
reported having a birth before age 12, had a birth before marriage, or
duration between births of less than nine months.
Finally, I restrict the sample to Hindus,
who constitute about 80\% of India's population.

Recall error is heavily dependent on how long ago a woman was married.
I, therefore, drop women married 22 years or more 
for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
and 25 years for NFHS-3 and NFHS-4.
The final sample consists of 
\input{../tables/num_women.tex}
% [number] women, with [number] parity one through four births.

The first spell begins at the month of marriage.

The second and subsequent spells begin nine months after the previous birth 
because that is the earliest we should expect to observe a new birth.

All spells continue until either a child is born or censoring occurs.
Censoring can happen for three reasons:
the survey takes place;
sterilization of the woman or her husband;
or too few births are observed for the method to work.

@@

\begin{block}{Conclusion}

>>>>

The model is a discrete time, non-proportional, competing risk 
hazard model with two exit states: either a boy or a girl is born.
\begin{description}
\item[Competing risk] captures that
parents can choose the sex of children born with access to prenatal 
sex determination.
\item[Non-proportional hazard] captures that sex composition and 
the use of sex selection likely affect the shape of the hazard 
functions across groups.
\end{description}

The data come from the four rounds of the National Family Health Survey.
Sample is restricted to Hindu women who are married and regular residents of
the household and where all needed information are available.
Because of recall error, I drop women married 22 years or more 
for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
and 25 years for NFHS-3 and NFHS-4.
The final sample consists of 
\input{../tables/num_women.tex}
% [number] women, with [number] parity one through four births.

The first spell begins at the month of marriage, whereas the second and 
subsequent spells begin nine months after the previous birth.
All spells continue until either a child is born or censoring occurs.

@@

@@

\begin{alertblock}{Conclusion}
